---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# About

[![Travis-CI Build Status](https://travis-ci.org/jjchern/geocorr.svg?branch=master)](https://travis-ci.org/jjchern/geocorr)

`geocorr` is an R data package for a set of geographic crosswalk files 
generated from the Missouri Census Data Center's [**Geo**graphic **Corr**espondence Engine: `MABLE/Geocorr14`](http://mcdc.missouri.edu/websas/geocorr14.html). 

So far `geocorr` has six datasets:

- `geocorr::county2010_to_puma2000`: County10-PUMA00 Crosswalk File
- `geocorr::county2010_to_puma2012`: County10-PUMA12 Crosswalk File
- `geocorr::county2014_to_puma2000`: County14-PUMA00 Crosswalk File
- `geocorr::county2014_to_puma2012`: County14-PUMA12 Crosswalk File
- `geocorr::county2010_to_puma2000_pop14`: County10-PUMA00 Crosswalk File, with 2014 population as weights
- `geocorr::county2010_to_puma2012_pop14`: County10-PUMA12 Crosswalk File, with 2014 population as weights

The raw csv files, generated directly from [`MABLE/Geocorr14`](http://mcdc.missouri.edu/websas/geocorr14.html),
can be found in the [`\data-raw\` folder](https://github.com/jjchern/geocorr/tree/master/data-raw).

# Installation

```R
# install.packages("devtools")
devtools::install_github("jjchern/geocorr")

# To uninstall the package, use:
# remove.packages("geocorr")
```

# Usage

```{r}
library(dplyr, warn.conflicts = FALSE)
geocorr::county2010_to_puma2000
geocorr::county2010_to_puma2012
geocorr::county2014_to_puma2000
geocorr::county2014_to_puma2012
geocorr::county2010_to_puma2000_pop14
geocorr::county2010_to_puma2012_pop14
```

# Reference

- [IPUMA: Description of PUMA](https://usa.ipums.org/usa-action/variables/PUMA)
- [PSC: Creating County-Level Statistics from Public Use Microdata Areas (PUMAS)](http://www.psc.isr.umich.edu/dis/census/Features/puma2cnty/)
